Landau quantization of nearly degenerate bands

### 2018-09-19 paper.tex
Updates from ShareLaTeX

\begin{figure}
\includegraphics[width=0.8\columnwidth]{blochsphere.png}
\caption{Energy dependence of the Berry phase for inner [(a)] and outer [(b)] orbit. The Berry phase equals half the solid angle enclosed by the corresponding loop on the Bloch sphere \textbf{[loop must be explained, right-hand rule explained]}. The directions of the loops are indicated by black arrows and the black arrow outside of the sphere indicates increasing energy, where green lines correspond to $\epsilon_0$ in Eq. (\ref{whereisdiracpoint}) \textbf{This figure is problematic because only the red loop is shown, while for the other loops the audience is left guessing. Perhaps it is best to separate one bloch sphere into three smaller spheres, such that each smaller sphere has only one loop. We might also show the analog of Fig 3a for energy above and below Dirac point.}.\label{fig:blochsphere}}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=1.0\columnwidth]{blochsphere.png}
\caption{Energy dependence of the Berry phase for inner (upper panel) and outer (lower panel) orbits. For two band models, the Berry phase equals half the solid angle enclosed by the loop swept by spin orbit field on the unit sphere. The solid angles are indicated by blue outlines and the energy is measured from $\epsilon_0$ in Eq. (\ref{whereisdiracpoint}).\label{fig:blochsphere}}
\end{figure}
